%-------------------------
% Author: Luis Alcaras <luisalcarasr@gmail.com>
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/luisalcarasr}{\Large Luis Adrian Alcaras Rubalcava}} & Email: \href{mailto:luisalcarasr@gmail.com}{luisalcarasr@gmail.com}\\
  \href{https://github.com/luisalcarasr}{github.com/luisalcarasr} & Mobile: \href{tel:+524494363926}{+52 449 436 3926} \\
\end{tabular*}

%--------ABOUT ME------------
\section{About Me}
    {Software Engineer with 8 years of experience, specialized in web development and actively involved in all stages of the software development lifecycle. Passionate about technology from an early age, I pursued a degree in Systems Engineering. I’ve contributed to solutions in sectors like renewable energy and digital media, developing everything from statistical models to video processing systems. Currently, I collaborate with Data Science, Threat Research, and Bot Defense teams to build secure, high-impact products.}

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Frameworks: }{Flask (Python), React (TypeScript/JavaScript)}
    }
    \item{
      \textbf{Cloud Services: }{Google Cloud Platform (Cloud Run, BigQuery, Cloud Storage, App Engine, Compute Engine, Kubernetes Engine), Amazon Web Services (Lambda, S3), GitLab CI/CD}
    }
    \item{
      \textbf{Databases: }{PostgreSQL, Google Cloud Platform (BigQuery)}
    }
    \item{
      \textbf{Tools: }{Git, Docker, Vim}
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {\href{https://www.f5.com/}{F5}}{Aguascalientes, Mexico}
    {Software Engineer}{Aug 2017 -- Jan 2019}
    \resumeItemListStart

      \resumeItem{\href{https://www.f5.com/products/distributed-cloud-services/bot-defense}{Threat Analytics and Reporting}}
        {Contributed to the development of a cloud-based solution, designed to detect threats. Built data analysis tools using \textbf{Google Cloud Platform} services including \textbf{App Engine}, \textbf{Cloud Run}, \textbf{BigQuery}, and \textbf{Cloud Storage}. Developed and maintained web applications with \textbf{React} and \textbf{Flask}, and managed relational data with \textbf{PostgreSQL}. Collaborated cross-functionally to deliver scalable, data-driven insights and supported continuous improvement in threat detection capabilities.}

      \resumeItem{\href{https://www.f5.com/labs}{F5 Labs}}
        {Contributed to the development of data analysis tools supporting F5 Labs' research initiatives. Leveraged \textbf{Google Cloud Platform} services, including \textbf{Cloud Run} (Functions), \textbf{BigQuery}, and \textbf{Cloud Storage}, to build scalable data pipelines and automate threat intelligence processing. Collaborated with security researchers to design systems that enhance visibility into global cyber threats. Ensured solutions met performance, scalability, and security best practices within a cloud-native environment.}

    \resumeItemListEnd

  \resumeSubheading
    {\href{https://www.improving.com/}{Improving}}{Aguascalientes, Mexico}
    {Software Engineer}{Aug 2017 -- Jan 2019}
    \resumeItemListStart
      \resumeItem{\href{https://www.autodesk.com/products/info360-insight/overview}{Info360 Insight} (\href{https://www.autodesk.com/}{Autodesk})}
        {I contributed to the development of a cloud-based digital twin solution for water and wastewater utility operations. Utilizing \textbf{React}, \textbf{Webpack} Module Federation, \textbf{Flask}, and \textbf{PostgreSQL}, I played a key role in building scalable, real-time dashboards and analytics tools that integrate SCADA and IoT data. My work supported features such as customizable workspaces, incident management workflows, and advanced analytics, enabling utilities to monitor system performance, assess outage impacts, and automate compliance reporting. This project, hosted on \textbf{Amazon Web Services}, enhanced operational decision-making and streamlined regulatory compliance for utility providers.}
      \resumeItem{\href{https://www.j2inn.com/finframework}{FIN Framework} (\href{https://www.siemens.com/}{Siemens})}
        {Contributed to the development of an advanced software platform for smart buildings and IoT applications. Utilized \textbf{React} for building dynamic user interfaces, \textbf{PostgreSQL} for efficient data management, and \textbf{Flask} to develop robust backend services. Integrated \textbf{Amazon Web Services}, including \textbf{Edge2Cloud}, to enable secure, remote access and management of building automation systems. Collaborated with cross-functional teams to enhance system integration capabilities, supporting protocols like \textit{BACnet} and \textit{Modbus}, and implemented features for real-time monitoring, control, and analytics. Ensured compliance with cybersecurity standards, contributing to a scalable and secure solution for modern building management.}
      \resumeItem{\href{https://auxita.com/}{Auxita}}
        {I contributed to the development of a secure, EMR-integrated healthcare platform designed to streamline specialty care workflows by transforming patient data into actionable insights. Leveraging \textbf{React} for frontend development, \textbf{Flask} for backend services, and \textbf{PostgreSQL} for data management, I built scalable, cloud-native applications deployed on \textbf{Google Cloud Platform}. My work supported Auxita’s mission to reduce administrative burdens for healthcare providers, enhance patient support program integration, and improve clinical decision-making through real-time dashboards and digital prior authorization tools. This role required close collaboration with cross-functional teams to deliver a user-centric, compliant solution in the Canadian healthcare ecosystem.}
    \resumeItemListEnd

  \resumeSubheading
    {\href{https://www.softtek.com/}{Softtek}}{Aguascalientes, Mexico}
    {Software Engineer}{Jan 2019 -- May 2021}
    \resumeItemListStart

      \resumeItem{Cumulus (\href{https://www.gevernova.com/}{GE Renewable Energy})}
        {I contributed to the development and modernization of a data analytics platform for wind turbine performance. I was responsible for implementing a comprehensive turbine catalog, integrating noise and power curves based on real-world data using \textbf{Weibull distribution}. This enabled engineers to optimize turbine selection based on geographic and technical specifications. Originally built with PHP and Angular, I led the cloud migration to \textbf{Google Cloud Platform}, utilizing \textbf{BigQuery} for large-scale sensor data processing and \textbf{PostgreSQL} for modeling the turbine catalog. I developed a scalable backend with \textbf{Flask} and a modern frontend with \textbf{React}, both deployed on \textbf{App Engine}. The entire environment was containerized using \textbf{Docker}, ensuring portability, scalability, and efficient resource usage in the cloud.}
      \resumeItem{FourQ (\href{https://www.blackline.com/about/press-releases/2022/blackline-acquires-fourq-redefining-intercompany-financial-management/}{BlackLine})}
        {An intercompany financial management platform that automates accounting processes between legal entities within multinational corporations. It streamlines invoicing, payments, and tax optimization to improve efficiency and compliance. Built with \textbf{React}, \textbf{Flask}, and \textbf{PostgreSQL}, the app is containerized with \textbf{Docker} and deployed on \textbf{Google Cloud Platform} for scalability and reliability. FourQ helps companies reduce foreign exchange risk, optimize working capital, and enhance profitability through automated intercompany workflows and reporting.}
    \resumeItemListEnd

  \resumeSubheading
    {\href{https://cceo.com.mx/}{CCEO - Software Development}}{Aguascalientes, Mexico}
    {Software Engineer}{Aug 2017 -- Jan 2019}
    \resumeItemListStart

      \resumeItem{\href{https://piba.com.mx/}{Programa de Intervención Breve para Adolescentes}}
        {Designed and developed a comprehensive healthcare platform by implementing a secure \textbf{RESTful API} using \textbf{Flask}, alongside building responsive web and mobile applications with \textbf{React} and \textbf{React Native}. Features include encrypted patient clinical history, appointment scheduling, patient interview and follow-up forms, and a therapist-patient directory with role-based access control. Managed \textbf{PostgreSQL} databases and \textbf{Linux} server administration to ensure robust data security and system reliability. This solution supports adolescent mental health interventions, streamlining clinical workflows and enhancing patient care management in compliance with privacy standards.}
      \resumeItem{El Niño de los Burritos}
        {Developed a full-stack food ordering application leveraging \textbf{Flask} for the backend API and \textbf{React}/\textbf{React Native} for web and mobile interfaces, delivering a seamless user experience for ordering and managing burrito deliveries. Integrated intuitive UI/UX designs created with \textbf{Figma}, ensuring user-friendly navigation and visual appeal. Implemented real-time order tracking, menu catalog management, appointment scheduling, and role-based access control. Managed \textbf{PostgreSQL} database and \textbf{Linux} server infrastructure to maintain data integrity and optimize performance across platforms.}
    \resumeItemListEnd

  \resumeSubheading
    {\href{https://www.jmromo.com/}{J.M. Romo}}{Aguascalientes, Mexico}
    {IT Support Technician}{Jan 2014 -- Jun 2014}
    \resumeItemListStart

      \resumeItem{Maintenance and Support}
        {Responsible for hardware and software maintenance, network monitoring, and issue resolution to ensure the continuous operation of computer systems across the plant.}
      \resumeItem{Technology Infrastructure Management}
        {Managed equipment inventory and ensured operational readiness, contributing to the efficiency of production processes.}
      \resumeItem{On-Site Technical Support}
        {Provided real-time technical assistance directly on the production floor, equipped with safety gear, to troubleshoot and resolve workstation issues.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source Python library for financial data analysis and machine learning for finance.}
%   \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://upa.edu.mx/}{Polytechnic University of Aguascalientes}}{Aguascalientes, Mexico}
      {Bachelor of Engineering in Strategic Information Systems}{Sep 2014 -- Apr 2019}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://cecytejalisco.edu.mx/}{College of Scientific and Technological Studies}}{Jalisco, Mexico}
      {High School Technical Degree in Informatics}{Aug 2011 -- Jun 2014}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://maps.app.goo.gl/BuQny3JCEST5XE4i9}{Institute of Computing and Systems of Aguascalientes}}{Aguascalientes, Mexico}
      {Technical Degree in Programming Analyst}{Aug 2009 -- Jun 2011}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}